Living on the edge: crop boundary effects on canola and wheat yields in Alberta

### 2021-09-07 Manuscript/manuscript.Rmd
Added "raster" test
- aggregate data into hexagons, run similar analysis

- Summary:
  - At the level of individual fields, there was substantial variation in yield with distance from the field boundary, as well as with harvest sequence and spatially within each field
  - Overall, however, the effect of field boundary on yield was inconsistent and the change in mean yield tended to be small ($\sim$0.5 T/ha for canola)

>>>>

At the level of individual fields, both average and SD of yield varied with distance from the field boundary.
Both metrics also varied with ground speed and harvest sequence, and there were strong spatial relationships within each field, likely related to underlying soil or moisture conditions.
However, the overall effect of field boundary on yield was inconsistent and the change tended to be small.
For example, average canola yield was $\sim$0.5 T/ha lower close to Standard field edges, and yield SD was $\sim$0.3 T/ha SD higher.

- Why no consistent effect for other boundary types? 
  - Our analysis only looks at boundary types, without considering larger landscape context (e.g. Lan's paper)
  - Boundary type itself is not well defined, so perhaps other metrics would be more helpful (height of veg, width of shelterbelt - I think this is important for hedgerows)
  - Ecosystem disservices (e.g. weeds, pest insects) could also be coming from field boundaries, which may negate any effect of ecosystem services; this is still poorly studied (but see Woodcock 2015)
  - Could vary by location; most fields were from central AB, but effects from southern AB may be confounding the signal
  - Additional confounding variables (crop history, differences in tillage)
